Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-14 article.tex
Modification des labels

    The fields that are being used here are described in Table~\ref{data_columns}.

\begin{table}[!b]
    \centering
    \caption{Description of the dataset}
    \label{data_columns}
    \begin{tabular}{ll}
        \toprule
        \textbf{Column} & \textbf{Description} \\
        \cmidrule(lr){1-2}
        \textsl{BS\_anfr\_id} & \acrshort{anfr} \acrshort{bs} ID \\ 
        \textsl{x, y, latitude, longitude} & Base station coordinates \\ 
        \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the \acrshort{bs} \\ 
        \bottomrule
    \end{tabular}
\end{table}

@@

A Delaunay triangulation of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
do not contain any of the points. You can find an illustration of this method in Figure~\ref{del_tri}.

@@

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_circumcircles_vectorial.png}}
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_Voronoi.png}}
    \caption{Example of a Delaunay triangulation (in black) and Voronoi tessellation (in red)}
    \label{del_tri}
\end{figure}

@@

For each base station the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in $\unit{km}$), thus making it possible to classify each base station into four different categories listed in Table~\ref{crit_summary}.

@@

\begin{table}[!b]
    \centering
    \caption{Summary of criteria values}
    \label{crit_summary}
    \begin{tabular}{clcc}
        \toprule
        \textbf{$\gamma_i$} & \textbf{Description} & \textbf{max\_distance} & \textbf{min\_angle} \\
        \cmidrule(lr){1-4}
        $\left[0, 1\right]$ & city center & $\unit[2]{km}$ & $5^\circ$ \\
        $\left]1, 2\right]$ & urban area & $\unit[5]{km}$ & $10^\circ$ \\
        $\left]2, 4\right]$ & extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
        $\left]4, \infty\right[$ & courntryside & $\unit[15]{km}$ & $20^\circ$ \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/points.png}
    \caption{Example of a Delaunay triangulation}
    \label{crit_pts}
\end{figure}

\begin{figure}[!b]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/distance_elim.png}
    \caption{Example of a Delaunay triangulation}
    \label{crit_dis}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/angle_elim.png}
    \caption{Example of a Delaunay triangulation}
    \label{crit_ang}
\end{figure}

\begin{figure}[!b]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}
    \caption{Example of a Delaunay triangulation}
    \label{crit_qua}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/neighs.png}
    \caption{Example of a Delaunay triangulation}
    \label{crit_nei}
\end{figure}

@@

\subsubsection{Angle criterion}
For each \acrshort{bs}, a potential neighbour can be \og hidden\fg{} by another one which nearer because there is a too narrow angle between those two \acrshort{bs}.
This criterion, will therefore suppress the longest edge between two \acrshort{bs} separated by a too small angle. This is illustrated in Figure \ref{crit_ang}.

>>>>

    The fields that are being used here are described in Table~\ref{table:data_columns}.

\begin{table}[!b]
    \centering
    \caption{Description of the dataset}
    \label{table:data_columns}
    \begin{tabular}{ll}
        \toprule
        \textbf{Column} & \textbf{Description} \\
        \cmidrule(lr){1-2}
        \textsl{BS\_anfr\_id} & \acrshort{anfr} \acrshort{bs} ID \\ 
        \textsl{x, y, latitude, longitude} & Base station coordinates \\ 
        \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the \acrshort{bs} \\ 
        \bottomrule
    \end{tabular}
\end{table}

@@

A Delaunay triangulation of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
do not contain any of the points. You can find an illustration of this method in Figure~\ref{fig:del_tri}.

@@

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_circumcircles_vectorial.png}}
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_Voronoi.png}}
    \caption{Example of a Delaunay triangulation (in black) and Voronoi tessellation (in red)}
    \label{fig:del_tri}
\end{figure}

@@

For each base station the mean distance to its three nearest neighbours is calculated (we will call this value $\gamma_i$, in $\unit{km}$), thus making it possible to classify each base station into four different categories listed in Table~\ref{table:crit_summary}.

@@

\begin{table}[!b]
    \centering
    \caption{Summary of criteria values}
    \label{table:crit_summary}
    \begin{tabular}{clcc}
        \toprule
        \textbf{$\gamma_i$} & \textbf{Description} & \textbf{max\_distance} & \textbf{min\_angle} \\
        \cmidrule(lr){1-4}
        $\left[0, 1\right]$ & city center & $\unit[2]{km}$ & $5^\circ$ \\
        $\left]1, 2\right]$ & urban area & $\unit[5]{km}$ & $10^\circ$ \\
        $\left]2, 4\right]$ & extra-urban area & $\unit[10]{km}$ & $15^\circ$ \\
        $\left]4, \infty\right[$ & courntryside & $\unit[15]{km}$ & $20^\circ$ \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/points.png}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_pts}
\end{figure}

\begin{figure}[!b]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/distance_elim.png}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_dis}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/angle_elim.png}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_ang}
\end{figure}

\begin{figure}[!b]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_qua}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{images/illus_crit/neighs.png}
    \caption{Example of a Delaunay triangulation}
    \label{table:crit_nei}
\end{figure}

@@

\subsubsection{Angle criterion}
For each \acrshort{bs}, a potential neighbour can be \og hidden\fg{} by another one which nearer because there is a too narrow angle between those two \acrshort{bs}.
This criterion, will therefore suppress the longest edge between two \acrshort{bs} separated by a too small angle. This is illustrated in Figure \ref{table:crit_ang}.
